\section{Who Am I?}

\ftc{Who Am I?}

%\subsection{What I learned?}
%\ftc{What I learned?}
\frame{\frametitle{What I learned?}
\begin{itemize}
\item[] {}
\item {2007$\sim$present: (learning) Haskell}
\item {2006$\sim$present: Ruby}
\item {2005$\sim$2008: C++}
\item {2001$\sim$2004: C}
\item[] {}
\end{itemize}
}

%\subsection{What I worked?}

%\ftc{What I worked?}
\frame{\frametitle{What I worked?}
\begin{itemize}
\item[] {}
\item[] {}
\item \jref{http://roodo.com}{roodo.com}
\item \jref{http://cardinalblue.com}{cardinalblue.com}
\item[] {}
\item[] {}
\end{itemize}
}

%\subsection{Where you can find me}

%\ftc{Where you can find me}
\frame{\frametitle{Where you can find me}
\begin{itemize}
\item[] {}
\item \jref{https://github.com/godfat}{github.com/godfat}
\item \jref{https://twitter.com/godfat}{twitter.com/godfat}
\item \jref{https://profiles.google.com/godfat}{profiles.google.com/godfat}
\item[] {}
\item[] {}
\end{itemize}
}

%\subsection{How I started to learn Haskell}

%\ftc{How I started to learn Haskell}
\frame{\frametitle{How I started to learn Haskell}
\begin{itemize}
\item[] {}
\item <1->{PLT at {\usebeamerfont*{font DejaVu Sans Mono}{ssh://bbs@ptt.cc}} }
\item <2->{IIS at Sinica}
\item <3>{FLOLAC}
\item[] {}
\item[] {}
\end{itemize}
}

%%%%%%  section break line %%%%%% 

\section{Table of Contents}
%\ftc{Table of Contents}
\frame{\frametitle{Table of Contents}
    \begin{itemize}
      \item {What can Haskell do?}
      \item {What is λ-Calculus?}
      \item {Why Implement λ-Calculus?}
      \item {Let's Implement λ-Calculus}
      \item {Questions?}
      \item {References}
    \end{itemize}
}

%%%%%%  section break line %%%%%% 
\section{What can Haskell do?}
%\ftc{What can Haskell do?}
%%%% special case!
% \frame{\vskip 12mm%
% \frametitlecenter{What can\\Haskell do?}
% }
\frame{\frametitle{Table of Contents}
  \begin{itemize}
    \item {What can Haskell do?}
    \item {\color{lightgray} What is λ-Calculus?}
    \item {\color{lightgray} Why Implement λ-Calculus?}
    \item {\color{lightgray} Let's Implement λ-Calculus}
    \item {\color{lightgray} Questions?}
    \item {\color{lightgray} References}
  \end{itemize}
}


\ftc{Defined in 1990}

% \ftc{Successor of Miranda from 1985} 
%%%% special case!
\frame{\vskip 22mm%
\frametitlecenter{Successor of Miranda from 1985}
}

\ftc{Haskell 98}

\ftc{Haskell 2010}

%\ftc{GHC (Glasgow Haskell Compiler)}
\frame{\frametitle{GHC (Glasgow Haskell Compiler)}
\begin{itemize}
  \item[]{}
  \item<1->{STM {\normalsize (Software Transactional Memory)}}
  \item<2->{Template Haskell}
  \item<3->{GADT {\normalsize (Generalized Algebraic Data Type)}}
  \item[]{}
  \item[]{}
\end{itemize}
}

%\ftc{Notable Projects}
\frame{\frametitle{Notable Projects}
\begin{itemize}
  \item[]{}
  \item<1->{Audrey Tang's ({\usebeamerfont*{font Hiragino Maru Gothic}{唐鳳}}) Pugs}
  \item<2->{xmonad}
  \item<3->{Darcs}
  \item[]{}
  \item[]{}
\end{itemize}
}

%\ftc{Parallelism vs Concurrency?}
\frame{\frametitle{Parallelism vs Concurrency?}
\begin{itemize}
  \item[]{}
  \item<1->{\jref{http://community.haskell.org/~simonmar/par-tutorial.pdf}{par-tutorial} }
  \item<2->{\jref{http://ghcmutterings.wordpress.com/2009/10/06/parallelism-concurrency/}
           {Parallelism $\neq$ Concurrency} }
  \item<3->{\jref{http://existentialtype.wordpress.com/2011/03/17/parallelism-is-not-concurrency/}
           {Parallelism is not concurrency} }
  \item[]{}
  \item[]{}
\end{itemize}
}
